---
title: "BattlefieldV_Report"
author: '@jasonmstevens'
date: "January 13, 2019"
output:
  html_document:
    theme: journal
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## A Data Science Journey through Battlefield V

Here is some text

```{r setup}

library(tidyverse)
library(readxl)
library(lubridate)

BFV <- read_xlsx("D:/Data_Science/BattlefieldV/Battlefield5.xlsx", sheet = "Sheet1") %>%
  filter(!is.na(Date))

ROWS <- nrow(BFV)
AVG_KD <- mean(as.numeric(BFV$`K/D`), na.rm = TRUE)
AVG_KD <- round(AVG_KD, digits = 3)
Total_KD <- sum(as.numeric(BFV$Kills), na.rm = TRUE)/sum(as.numeric(BFV$Deaths), na.rm = TRUE)
Total_KD <- round(Total_KD, digits = 3)
Kills <- sum(as.numeric(BFV$Kills), na.rm = TRUE)
Deaths <- sum(as.numeric(BFV$Deaths), na.rm = TRUE)

DAY <- today(tzone = "America/New_York")

PlayRange <- range(BFV$Date, na.rm = TRUE)

```

### A Snapshot of my Play Style and Skill

Here is a breif overview of what kind of player I am. Mostly, I play for fun and the challenge the game offers. As can be seen below I would consider myself a mediocre player. 

```{r Overview_Stats, echo=FALSE}

paste0("I've tracked a total of ", ROWS, " rounds. During that the interval I've averaged a K/D of ", AVG_KD,
       " and a total K/D of ", Total_KD, " (Kills = ", Kills, ", Deaths = ", Deaths, ").")


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r Overview_Plot, echo=FALSE}

Overview_Plot <- ggplot(BFV, aes())+
  geom_bar(aes(GameMode, fill = Weapon))+
  facet_wrap(~Class)
  

Overview_Plot

```
